---
title: "Report on Gun Murders"
author: "Rafael Irizarry"
date: "5/1/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a report on 2010 gun murder rates obtained from FBI reports. The original data was obtained from [this Wikipedia page](https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state).

We are going to use the following library:

```{r loading-libs, message=FALSE, echo=TRUE, warning=FALSE}
library(tidyverse)
```
  
and load the data we already wrangled:

```{r}
load("rda/murders.rda")
```

## Murder rate by state 

We note the large state to state variability by generating a barplot showing the murder rate by state:

```{r murder-rate-by-state, echo=FALSE}
murders %>% mutate(abb = reorder(abb, rate)) %>%
  ggplot(aes(abb, rate)) +
  geom_bar(width = 0.5, stat = "identity", color = "black") +
  coord_flip()
```

## Shrinking core model

$$x(t, R) = 1- (1-\frac{t}{\tau})^3; t \le \tau$$
Where $x(t,R)$ is the fraction reacted at elapsed time $t$ (particle of radius $R$), $t$ is time, $R$ particle radius, $\tau$ is the time required for complete reaction:
$$\tau = \frac{K*Au*R}{[CN^-]}$$

```{r, echo=FALSE}
summary(murders)
```

```{r, echo=F}
n <- nrow(mtcars)
```
Here `r n` cars are compared


```{r eval=FALSE}
a <- 2
```

```{r include=FALSE}
print("Hello World!")
a <- 5
```

```{r echo=FALSE}
a <- a+1
print(a)
```